Supplementary Figure 5b

### 2018-05-17 inst/supp_figure5b/supp_figure5b.Rmd
removing supp 5b and updating fig nrs

---
title: "Supplementary Figure 5c"
subtitle: "Monitoring proliferation of miR34a asRNA overexpressings cells under conditions of starvation"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

@@

data <- getData("Supplementary Figure 5c")

@@

#calculate mean normalized flouresence for each condition and biological replicate
subDataMeans <- subData %>%
  group_by(cellLine, Time, Condition, `Biological replicate`) %>%
  summarize(mean = mean(violetNorm)) %>%
  ungroup()

#model each condition using the mean of all biological replicates using a lm
model.info <- subDataMeans %>%
  group_by(Condition) %>%
  do(glance(lm(mean ~ poly(Time, 3) + cellLine, data = .))) %>%
  ungroup()

@@

```{r, fig.align='center', fig.height=8, fig.width=12}
p <- subDataMeans %>% 
  mutate(Condition = parse_factor(Condition, levels = c("RPMI", "0.1% FBS", "HBSS"))) %>% 
  ggplot() + 
  geom_smooth(
    aes(Time, mean, colour = cellLine, group = cellLine), colour = "lightgrey",
    method = "lm", formula = y ~ poly(x, 3), size = 0.5, alpha = 0.1
  ) +
  geom_boxplot(
    aes(Time, mean, colour = cellLine, group = interaction(Time, cellLine)),
    fatten = 2, lwd = 0.2
  ) +
  facet_wrap(~Condition) + 
  scale_x_continuous(breaks = c(0, 24, 48, 72)) +
  labs(
    x = "Time (hours)", 
    y = "Mean \U0394 fluorescence intensity"
  ) + 
  guides(colour = guide_legend(title = "Cell line"))

@@

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Supplementary Figure 5c"][[1]])
ggsave(
  plot = figure,
  filename = path,
  device = cairo_pdf,
  height = 60,
  width = 100,
  units = "mm"
)
```

>>>>

---
title: "Supplementary Figure 5b"
subtitle: "Monitoring proliferation of miR34a asRNA overexpressings cells under conditions of starvation"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

@@

data <- getData("Supplementary Figure 5b")

@@

#calculate mean normalized flouresence for each condition and biological replicate
subDataMeans <- subData %>%
  group_by(cellLine, Time, Condition, `Biological replicate`) %>%
  summarize(mean = mean(violetNorm)) %>%
  ungroup()
```

Show stained vs. Unstained
```{r, fig.align="center", fig.width=10, fig.height=8}
data %>%
  ggplot() +
  geom_histogram(aes(Violet, fill = Type), alpha = 1/2, position = position_dodge(), binwidth = 0.01) +
  theme_bw() +
  scale_x_log10() +
  labs(x = "log10(Fluorescence intensity)", y = "Count") +
  facet_wrap(~Time)
```

Show time 0
```{r, fig.align="center", fig.width=10, fig.height=8}
data %>%
  filter(Time == 0) %>%
  unite(Sample, c("Cell line", "Biological replicate")) %>%
  mutate(Sample = case_when(
    str_detect(Sample, "unstained-F4") ~ "unstained-lncTAM34a",
    str_detect(Sample, "unstained-mock") ~ "unstained-mock",
    TRUE ~ Sample
  )) %>%
  select(Sample, Violet) %>%
  distinct() %>%
  ggplot() +
  geom_boxplot(aes(Sample, Violet)) +
  scale_y_log10() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x = "Sample_replicate", y = "log10(Fluorescence intensity)") +
  theme_bw()
```

Show fluorescence loss over time
```{r, fig.align="center", fig.width=10, fig.height=8}
data %>%
  mutate(Condition = if_else(Time == "0", "RPMI", Condition)) %>%
  ggplot() +
  geom_boxplot(aes(Time, Violet)) +
  facet_wrap(~Type) +
  scale_y_log10() +
  labs(y = "log10(Fluorescence intensity)") +
  theme_bw()
```

Show fluorescence per condition
```{r, fig.align="center", fig.width=10, fig.height=8}
data %>%
  filter(Type == "stained") %>%
  filter(Time != "0") %>%
  mutate(Condition = parse_factor(Condition, levels = c("RPMI", "0.1% FBS", "HBSS"))) %>%
  ggplot() +
  geom_boxplot(aes(Time, Violet)) +
  facet_wrap(~Condition) +
  theme_bw() +
  scale_y_log10() +
  labs(y = "log10(Fluorescence intensity)")
```

Show polynomial model info
```{r}
#model each condition using the mean of all biological replicates using a lm
model.info <- subDataMeans %>%
  group_by(Condition) %>%
  do(glance(lm(mean ~ poly(Time, 3) + cellLine, data = .))) %>%
  ungroup()

@@

```{r, eval = FALSE}
subData %>% 
  select(-Violet, -day0Violet) %>% 
  nest(violetNorm) %>% 
  spread(Time, data) %>% 
  mutate(`24-0` = map2_dbl(`0`, `24`, function(x, y) mean(unlist(y) - unlist(x)))) %>% 
  mutate(`48-24` = map2_dbl(`24`, `48`, function(x, y) mean(unlist(y) - unlist(x)))) %>% 
  mutate(`72-48` = map2_dbl(`48`, `72`, function(x, y) mean(unlist(y) - unlist(x)))) %>% 
  select(-(`0`:`72`)) %>% 
  gather(Time, diff, -(Type:cellLine)) %>% 
  group_by(Condition, Time) %>% 
  summarize(m = mean(diff))

subDataMeans %>% 
  spread(cellLine, mean) %>% 
  mutate(diff = lncTAM34a - mock) %>% 
  group_by(Time, Condition) %>% 
  summarize(meanDiff = mean(diff)) %>% 
  print(n = nrow(.))
```

Plot final figure
```{r, fig.align='center', fig.height=8, fig.width=12}
p <- subDataMeans %>% 
  mutate(Condition = parse_factor(Condition, levels = c("RPMI", "0.1% FBS", "HBSS"))) %>% 
  ggplot() + 
  geom_smooth(
    aes(Time, mean, colour = cellLine, group = cellLine), colour = "lightgrey",
    method = "lm", formula = y ~ poly(x, 3), size = 0.5, alpha = 0.1
  ) +
  geom_boxplot(
    aes(Time, mean, colour = cellLine, group = interaction(Time, cellLine)),
    fatten = 2, lwd = 0.2
  ) +
  facet_wrap(~Condition) + 
  scale_x_continuous(breaks = c(0, 24, 48, 72)) +
  labs(
    x = "Time (hours)", 
    y = "Mean \U0394 fluorescence intensity"
  ) + 
  guides(colour = guide_legend(title = "Cell line"))

@@

#path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Supplementary Figure 5b"][[1]])
#ggsave(
#  plot = figure,
#  filename = path,
#  device = cairo_pdf,
#  height = 60,
#  width = 100,
#  units = "mm"
#)
```
